Continuous Generalization of Buildings \\ by Growing and Aggregating

### 2017-09-18 ContinuousGeneralisation_Paper/ContinuousGeneralisation_Paper_Sigspatial/ContinuousGeneralisation_Paper_Sigspatial.tex
polished section of methodology

\begin{abstract}
To enable smooth zooming, we propose a method to continuously 
generalize buildings from a given start map to a smaller-scale goal map, where 
there are only built-up area polygons instead of individual building polygons.
For the sake of convenience, 
we name the buildings on the start map \emph{original buildings}.
%
For an intermediate scale, 
we aggregate the original buildings that will be too close 
by introducing bridges.
We grow (bridge) original buildings based on buffering 
and simplify the grown buildings.
We take into account the shapes of the buildings 
both at the previous map and goal map to make sure that 
the buildings are always growing.
%
\newline\indent
The advantages of our method are as follows. 
First, the buildings grow continuously 
and, at the same time, are simplified.
Second, right angles of buildings are preserved during growing: the merged 
buildings still look like buildings. 
Third, the distances between buildings are 
always larger than a specified threshold.
We do a case study to show the performances of our method.
\end{abstract}

>>>>

\begin{abstract}
To enable smooth zooming, we propose a method to continuously 
generalize buildings from a given start map to a smaller-scale goal map, where 
there are only built-up area polygons instead of individual building polygons.
We name the buildings on the start map \emph{original buildings}.
%
For an intermediate scale, 
we aggregate the original buildings that will become too close 
by adding bridges.
We grow (bridge) original buildings based on buffering 
and simplify the grown buildings.
We take into account the shapes of the buildings 
both at the previous map and goal map to make sure that 
the buildings are always growing.
%
\newline\indent
The advantages of our method are as follows. 
First, the buildings grow continuously 
and, at the same time, are simplified.
Second, right angles of buildings are preserved during growing: the merged 
buildings still look like buildings. 
Third, the distances between buildings are 
always larger than a specified threshold.
We do a case study to show the performances of our method.
\end{abstract}
